---
title: "Child Care Analysis"
output: html_notebook
---

```{r}

install.packages("fuzzyjoin")

library(tidyverse)
library(profilr)
library(magrittr)
library(fuzzyjoin)

childCare <- read_csv("data/Licensed_Child_Care_Providers_and_Facilities.csv")
schools <- read_csv("data/School_Directory.csv")

#profiling the data to see interesting patterns
#profiledChildCare <- profile(childCare) %>% select(.column_name,.count_elements,.count_uniques,.count_NAs,.percent_NAs,.top_5_values,.bottom_5_values)
#profiledSchool <- profile(schools) %>% select(.column_name,.count_elements,.count_uniques,.count_NAs,.percent_NAs,.top_5_values,.bottom_5_values)
```
## Findings from wikipedia
* Child care usually from age six weeks to age thirteen.

## Some interesting questions that might be answerable
* how much hours of salary needed to pay daycare
* are the centers flexible?
* cost of childcare? Can people move to a different childcare which cost less
* How many schools provide childcare - why and why not?

## Plots
* no of childCare centers per county

```{r}

#Since the school dataset spans over multiple year. Choose only one year, in this case recent one
schools2016 <- schools %>% filter(SchoolYear == "2016") %>% mutate(UpperSchoolName = toupper(SchoolName))


#Factors are not joinable in dplyr. Convert them to character vector
tst$SchoolName <- as.character(tst$SchoolName)

# Add a control column to the dataset. Once we make a join, the success of the join can be verified by comparing this column. A true in this column should have a school value most of the time
childCare %<>% mutate(As_of_Year = "2016", ProbablySchool = grepl("@",Name) | grepl(" AT ",Name)) %>% select(Name,ProbablySchool,everything())

# Create a lookup dataset with possible Chilcare Name and school name association
schoolLookup <- childCare %>% select(Name) %>%  regex_inner_join(schools2016,by=c(Name = "UpperSchoolName")) %>% select(Name,UpperSchoolName)  %>% rename(childCareName = Name, SchoolName = UpperSchoolName)

#left join the school dataset with the lookup
childCare %>% left_join(schoolLookup,by = c("Name" = "childCareName")) %>% select(Name,ProbablySchool,SchoolName) %>% filter(ProbablySchool == TRUE)

#write the new dataset to data folder for analysis
write_csv(childCare,"data/ChildcareAndSchools.csv")
```
